Automating Verification of MPC Security

### 2023-06-15 popl24/composition.tex
checkpoint

A basic intuition about how garbled gates work is that they are
``nearly'' passive secure, modulo the feature that outputs of
individual logic gates in circuits are encryped. That is, each gate
enjoys $\NIMO$, except the output is not in the clear, but correlated
with the flips that the garbler sampled for the gate's output wire
label, both key and pointer bits. We call this \emph{Garbled $\NIMO$},
or $\gNIMO$. To clarify this definition, recall that Definition \ref{def-progd}
posits a variable $\itv$ to refer to the expression $\be$ when
considering the distribution $\progd(\prog,\be)$.
\begin{definition}[Garbled $\NIMO$]
  We write $\gNIMO(\prog,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} =
  \be_{\ttt{p}}\}, g)$ with $\iov(\prog) = S \cup V$ iff for all $H$,
  $C$ with $|C| \le |H|$, for all $\store \in
  \mems(S_C \cup V_C)$, and for all $\stores$ with domain $X = S_C \cup V_C
    \cup \{ \itv, \flip{2}{\ttt{gate:}g.w} \}$ for both $w \in \{\ttt{p},\ttt{k}\}$, such that:
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store(\itv) = \store(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  or
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store(\itv) = \neg\store(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  %where for any $\beta$:
  %$$\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \beta \}$$
  %or
  %$$
  %\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \neg\beta \}
  %$$
  we have:
  $$
  \margd{(\condd{\progd(\prog,\be_w)}{\stores_{X-{V_C}}})}{S_H} =
  \margd{(\condd{\progd(\prog,\be_w)}{\stores})}{S_H}
  $$
\end{definition}

>>>>

A basic intuition about how garbled gates work is that they are
``nearly'' passive secure, modulo the feature that outputs of
individual logic gates in circuits are encryped. That is, each gate
enjoys $\NIMO$, except the output is not in the clear, but correlated
with the flips that the garbler sampled for the gate's output wire
label, both key and pointer bits. We call this \emph{Garbled $\NIMO$},
or $\gNIMO$. To clarify this definition, recall that Definition \ref{def-progd}
posits a variable $\itv$ to refer to the expression $\be$ when
considering the distribution $\progd(\prog,\be)$.
\begin{definition}[Garbled $\NIMO$]
  We write $\gNIMO(\prog,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} =
  \be_{\ttt{p}}\}, g)$ with $\iov(\prog) = S \cup V$ iff for all $H$,
  $C$ with $|C| \le |H|$, for all $\store \in \mems(S_C \cup V_C)$,
  for both $w \in \{\ttt{p},\ttt{k}\}$, and for all $\stores$ with
  domain $X = S_C \cup V_C \cup \{ \itv, \flip{2}{\ttt{gate:}g.w} \}$
  such that:
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store'(\itv) = \store'(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  or
  $$
  \stores = \{ \store' \mid \store \subset \store' \wedge 
  \store'(\itv) = \neg\store'(\flip{2}{\ttt{gate:}g.w}) \} 
  $$
  %where for any $\beta$:
  %$$\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \beta \}$$
  %or
  %$$
  %\store^2 = \store\{ \flip{2}{\ttt{gate:}g.w} \mapsto \beta \}\{ \itv \mapsto \neg\beta \}
  %$$
  we have:
  $$
  \margd{(\condd{\progd(\prog,\be_w)}{\stores_{X-{V_C}}})}{S_H} =
  \margd{(\condd{\progd(\prog,\be_w)}{\stores})}{S_H}
  $$
\end{definition}

\begin{lemma}
  \label{lemma-scope}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
  and $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ then
  $(\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_2)})$
  for any $\prog_1'$ where $\flips(\prog_1') \cap \flips(\prog_2) = \varnothing$.
\end{lemma}
